Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-26 graviton spectra/content/br.tex
merge

\newcommand\til{\widetilde}
\begin{document} 
\section{Twisted AdS space}
\label{sec:ads}

@@

In \cite{CLsugra}, Costello and Li gave a rigorous definition of what it means to {\em twist} supergravity, which is nicely compatible with the mathematically more familiar notion of twisting supersymmetric gauge theories \cite{WittenTwist}.
In physical terms, twisted supergravity is supergravity in a background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge.
In principle, one can take the supercharge to be any square-zero covariantly constant spinor (so it satisfies the equations of motion of supergravity).
A class of such supercharges lie in the supersymmetry algebra.

@@

We similarly introduce an analog of the ${\mr AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity.
We begin with our twisted theory defined on
\[
\R \times \operatorname{Tot}(K_{\C^3}^{1/2}\otimes \C^2 \to X)
\]
with $X$ a complex threefold as in \eqref{eqn:thfm5}.
As above, we will momentarily be only concerned with flat space which means taking $X = \C^3$.
We once again will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/2}_{X}\otimes \C^2$, and we use $t$ to denote a fiber coordinate on $\R$.

>>>>

\begin{document} 
\section{Twisted AdS space}
\label{sec:ads}

@@

@@

We similarly introduce an analog of the ${\mr AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity.
We begin with our twisted theory defined on
\[
\R \times \operatorname{Tot}(K_{X}^{1/2}\otimes \C^2 \to X)
\]
with $X$ a complex threefold as in \eqref{eqn:thfm5}.
As above, we will momentarily be only concerned with flat space which means taking $X = \C^3$.
We once again will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/2}_{X}\otimes \C^2$, and we use $t$ to denote a fiber coordinate on $\R$.
